### 2012-03-07 paper.tex
Reformulation of a small paragraph

The oscillation period increases with time and becomes increasingly less stable as shown in Figure~\ref{fgr:extracts}. This phenomena is consistent across all measured samples. The large scatter in oscillation period can be attributed to the smaller oscillations in between on/off cycles. Occasionally, these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period. A possible explanation of the phenomenon could be sintering or roughening of the clusters. However, due to the fact that the overall conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause since this would also be expected to reduce the overall activity of the sample.

>>>>

The oscillation period increases with time and becomes increasingly less stable as shown in Figure~\ref{fgr:extracts}. This phenomena is consistent across all measured samples. The large scatter in oscillation period can be attributed to the smaller oscillations in between on/off cycles. Occasionally, these small amplitude oscillations will trigger a full switch thus introducing more short-period oscillations despite the trend of increasingly slower oscillation period. This could suggest either sintering or roughening of the clusters. However, since the average conversion integrated over full oscillation periods is constant we do not expect sintering to be the cause where an average loss in activity of the sample would be expected.
